Deeply Virtual Compton Scattering measurement off bound protons

### 2018-11-27 eg6-letters/incoherent/incoherent_prl.tex
implement the comment from the clas collaboration review

\date{\today}
\begin{abstract}
 We report the first beam spin asymmetry (BSA) measurement of incoherent deeply 
   virtual Compton scattering (DVCS) off $^4$He. The data were accumulated 
   using a 6 GeV longitudinally polarized electron beam incident on a 
   pressurized $^4$He gaseous target placed in front of the CLAS spectrometer 
   in Hall-B at the Thomas Jefferson National Accelerator Facility. The 
   azimuthal angular ($\phi$) dependence of the BSA is studied in a wide range 
   of virtual photon and scattered proton kinematics. The Q$^2$, $x_B$, and $t$ 
   dependencies of the BSA on the bound proton are compared with those on the 
   free proton. In the whole kinematical region of our measurements, the BSA on 
   the bound proton is smaller by $20\%$ to $40\%$, indicating possible medium 
   modification of its partonic structure. This measurement opens a new avenue 
   for studying structure of the bound nucleon and explore the origin of the 
   EMC effect using the framework of the generalized parton distributions.

@@

A wealth of information on the structure of hadrons lies in the correlations 
between the momentum and spatial degrees of freedom of the partons. These 
correlations can be revealed through deeply virtual Compton scattering (DVCS), 
i.e., the hard exclusive lepto-production of a real photon, which provides 
access to a three-dimensional imaging of partons within the generalized parton 
distributions (GPDs) framework 
\cite{Mueller:1998fv,Ji:1996ek,Ji:1996nm,Radyushkin:1996nd,Radyushkin:1997ki}.   
The free proton DVCS measurement has been the focus of a worldwide effort 
\cite{Stepanyan:2001sm,Airapetian:2001yk,Airapetian:2006zr,Chekanov:2003ya,Aktas:2005ty,Chen:2006na,Munoz 
Camacho:2006hx,Girod:2007aa,Mazouz:2007aa,Gavalian:2009,Seder:2015,Pisano:2015,Jo:2015ema}
involving several accelerator facilities such as Jefferson Lab, DESY and  
CERN. These measurements now enable the extractions of GPDs 
and a 3-D tomography of the free proton \cite{Guidal:2013rya,Dupre:2016mai}.  
New measurements of DVCS from the $^{4}$He nucleus are a critical 
step towards providing a similar 3-D pictures of the quark structure of the 
nucleus~\cite{Dupre:2015jha}. In the nuclear case however, two channels are available,
the coherent channel where the scattering is off the entire nucleus, which is 
left intact in the final state \cite{Airapetian:2009cga,
Hattawy:2017woc}, and the incoherent channel where the DVCS happens on a 
nucleon, which is ejected from the nucleus.
The latter is the focus of this letter and provides a unique access to the 
modification of the partonic structure of the bound nucleons 
\cite{simonetta_2,Guzey:2006xi,Guzey:2008fe}. The 
$^{4}$He nucleus is an ideal experimental target for this measurement as it is 
characterized by a strong binding energy, a relatively high nuclear 
core density, and a large EMC effect~\cite{JSeely}. Moreover, it remains simple 
enough that precise calculation of its structure 
can be performed, making this nucleus the perfect target for our investigation of the 
medium modifications of the nucleon's partonic structure.

\begin{figure}[tb]
\includegraphics[width=7.5cm]{figs/handbag_incoherent.pdf}
\caption{Representation of the leading-order, twist-2, handbag diagram of the 
   incoherent DVCS process off $^4$He, where the four-vectors of the electrons, 
   photons, and protons are denoted by $k/k^\prime$, $q/q^\prime$, and 
   $p/p^\prime$, respectively. $x+\xi$ is the nucleon’s longitudinal momentum 
   fraction carried by the struck quark, 2$\xi$ is the longitudinal momentum 
   fraction of the momentum transfer $\Delta$ ($= q - q^\prime$), and 
   $t$~($=\Delta^2$) is the squared momentum transfer between the initial and
   the final state nucleon.}
\label{fig:diags}
\end{figure}

In this Letter, we present the first exclusive measurement of the beam-spin 
asymmetry (BSA) in deeply virtual electroproduction of a real photon off a bound 
proton in $^{4}$He. FIG.~\ref{fig:diags} illustrates the leading-twist handbag 
diagram for the DVCS process. In the Bjorken regime, i.e, large virtual photon 
four-momentum squared ($Q^{2}=-q^2=-(k-k^\prime)^2$), and at small invariant 
momentum transfer ($t=(q-q^\prime)^2$), the DVCS scattering process can be 
factorized, leaving the non-perturbative structure of the nucleon to be 
parameterized in terms of four chirally-even GPDs: $H$, $E$, $\widetilde{H}$, 
and $\widetilde{E}$, representing the four helicity-spin combinations of the 
quark-nucleon states \cite{Freund_Collins,Ji_Osborne}. Experimentally, we 
measure the squared sum of the Bethe-Heitler (BH) and the DVCS amplitudes. The 
BH process, where the real photon is emitted by the incident or the scattered 
electron rather than the nucleon, dominates the cross section at our 
kinematics. The BSA arises from the interference of these two terms and is 
directly sensitive to the DVCS amplitude that contains the information on the 
GPDs. Using a longitudinally polarized electron beam (L) and an unpolarized 
target (U), the BSA is defined as:
\begin{equation}
  A_{LU} = \frac{d^{5}\sigma^{+} - d^{5}\sigma^{-} }
                {d^{5}\sigma^{+} + d^{5}\sigma^{-}}.
    \label{BSA_equation}
  \end{equation}
where $d^{5}\sigma^{+}$($d^{5}\sigma^{-}$) is the photon electroproduction 
differential cross section for a positive (negative) beam helicity.

Following the cross section decomposition provided in \cite{Belitsky:2001ns}, 
the different components can be expressed in terms of Fourier coefficients 
associated with $\phi$-harmonics, where $\phi$ is the angle between the 
leptonic and the hadronic planes of the reaction. At leading-twist, the BSA can 
be parameterized as: 
\begin{equation}
   A_{LU}(\phi) = \frac{a_{0}\sin(\phi)}{1+a_{1}\cos(\phi)+a_{2}\cos(2\phi)}
   \label{eq:alu-simp}
\end{equation}
where the parameters $a_{0,1,2}$ are combinations of the above mentioned Fourier 
coefficients. The $\sin(\phi)$ harmonic is dominant in $A_{LU}$ 
and is proportional to the following combination of Compton form factors (CFF) 
\cite{Guidal:2013rya}
\begin{equation}
   a_{0} \propto \operatorname{Im}( F_1 \mathcal{H}- \frac{t}{4M^2} F_2 
   \mathcal{E}+ \frac{x_B}{2}(F_1+F_2)\tilde{\mathcal{H}})
\end{equation}
where $F_1$ and $F_2$ are the Dirac and Pauli form factors, respectively, and 
$x_B$ the Bjorken scaling variable. The real and the imaginary parts of the CFF 
$\mathcal{H}$ relate to the GPD $H$ as  \begin{align}
   \Re(&\mathcal{H}) = \mathcal{P} \int_{0}^{1}dx[H(x,\xi,t)-H(-x,\xi,t)] \, 
   C^{+}(x,\xi) \\
   \Im(&\mathcal{H}) = - \pi [H(\xi,\xi,t)-H(-\xi,\xi,t)],
\end{align}
with $\mathcal{P}$ the Cauchy principal value integral and $C^{+}$ a 
coefficient function defined as $(1/(x-\xi) + 1/(x+\xi))$, there $\xi$ is the 
skewing factor and can be related to $x_B$ by $\xi\approx {{x_B}\over{2-x_B}}$.  
Similar expressions apply for the GPDs $E$, $\widetilde{H}$, and 
$\widetilde{E}$.

@@

The experiment (E08-024~\cite{Hafidi:2008pr}) took place in Hall-B of Jefferson 
Lab using the nearly 100\% duty factor, longitudinally-polarized electron beam 
(83$\%$ polarization) from the Continuous Electron Beam Accelerator Facility 
(CEBAF) at an energy of 6.064 GeV. The data were accumulated over 
40 days using a 6-atm-pressure, 292-mm-long, and 6-mm-diameter gaseous $^4$He 
target centered at 64~cm upstream of the CEBAF Large Acceptance Spectrometer 
(CLAS) coordinate center. For DVCS experiments, the CLAS baseline design 
\cite{Mecking:2003zu} is supplemented with an inner calorimeter (IC) and a 
solenoid magnet. The IC extends the photon detection acceptance of CLAS down 
to a polar angle of 4$^{\circ}$. The 5-Tesla solenoid magnet in the center of 
which the target was located prevented the high-rate low-energy M{\o}ller 
electrons from reaching the CLAS drift chambers by guiding these electrons 
inside a tungsten shield placed around the beam line.

% DVCS selection
Incoherent DVCS events were selected by requiring an electron, a proton, and at 
least one photon in the final state. Electrons were identified as negatively 
charged tracks reconstructed in the drift chambers with an appropriate energy 
deposition in the electromagnetic calorimeter (EC) and a light yield above the 
threshold in the Cherenkov counters. The protons were identified from 
positively charged tracks based on their time-of-flight measured 
by the scintillator counters.  In addition, it was required that both the 
electron and the proton in the event originated from the same vertex at the 
target. The photons were detected in either the IC or the CLAS electromagnetic 
calorimeter. All the clusters within the IC fiducial region were assumed to be 
photons, while a timing cut is used to clean the EC photons from neutrons. Note 
that even though the DVCS reaction has only one real photon in the final state, 
events with more than one photon were not discarded at this stage. These extra 
photons are mostly soft photons from accidental coincidence which, as will be 
discussed below, the DVCS exclusivity cuts eliminate easily. In the following 
selection stage, the most energetic photon is considered as the DVCS photon 
candidate (see \cite{Hattawy:thesis} for additional details on the particles 
identification).

Further requirements were applied to clean the identified initial set of 
incoherent DVCS events from accidental and physics background events. First, 
events were selected with Q$^{2}$ greater than 1 GeV$^2$ to ensure the 
applicability of the DVCS handbag diagram, and with $\gamma^{*}p$ invariant 
mass (W$=\sqrt{(q+p)^2}$, assuming that the initial proton is at rest) greater 
than 2 GeV to avoid the nucleon resonance region.  The $t$, transferred 
momentum squared to the recoil proton, calculated from 4-momentum vectors of 
incoming and outgoing photons, was required to be greater than a minimum 
allowed value at given Q$^2$ and 
W~($t>t_{min}(~=-Q^{2}~\frac{2(1-~x_{B})(1~-~\sqrt{1~+~\epsilon^{2}})~+~\epsilon~^{2}}{4x_{B}(1-x_{B})+\epsilon^{2}}$,
where $\epsilon^{2}=~\frac{4M^{2}_{p}x^{2}_{B}}{Q^{2}}$ and $M_{p}$ is the 
proton mass). We specifically use the kinematics of the photons to determine 
$t$ because the initial proton kinematics is unknown due to Fermi motion. Then, 
we ensured the exclusivity of the incoherent DVCS events by imposing 
a series of constraints based on the four-momentum conservation 
in the reaction $ep\rightarrow e'p'\gamma$. These kinematical 
variables are: the coplanarity angle $\Delta\phi$ between the 
($\gamma,\gamma^*$) and ($\gamma^*$,$p'$) planes, the missing energy, mass, and 
transverse momentum of the $e'\gamma$ and $e'p'\gamma$ systems, the missing 
mass squared of the $e'p'$ system, and the angle $\theta$ between the measured 
photon and the missing momentum of the $e'p'$ system. The experimental data for 
the most relevant exclusivity variables are shown in FIG.~\ref{fig:kin-cuts}.  
Because of the Fermi motion of the nucleons in the helium nucleus, these cuts
are slightly wider than those previously used for free proton experiments~%
\cite{Girod:2007aa}. After the corrections discussed below, the asymmetries 
appear to be stable as a function of cut width and we see no sizable effect 
that can be related to the initial momentum of the nucleons. We also rejected 
events where a $\pi^0$ was identified by the invariant mass of two photons. At 
the end of this selection process, about 30k events passed all the 
requirements; their kinematic distributions are shown in 
FIG.~\ref{fig:kin-coverage}.

\begin{figure}[tb]
\includegraphics[width=8.9cm]{figs/incoh_exc_cuts_final.pdf}
\caption{The distributions 
   from left to right and from top to bottoms are: $\Delta \phi$, missing 
   energy, missing masses squared and the cone angle ($\theta$) between the 
   measured and the calculated photons in the $e'p'$ final-state system.
   The incoherent DVCS exclusivity cuts are represented by the vertical 
   red-dashed lines. The black distributions 
   represent the incoherent DVCS events candidate before the exclusivity 
   cuts. The shaded distributions represent the incoherent DVCS events which 
   passed all these cuts except the quantity plotted.}
\label{fig:kin-cuts}

@@

%background
The two main backgrounds that contribute to the event sample after the 
exclusivity cuts are due to accidental coincidences and exclusive $\pi^0$ 
production where one of the photons from the $\pi^0$ decay escapes the 
detection. The contribution from accidental events, i.e., $e'p'\gamma$ 
collections with particles originating from different electron scatterings, was 
evaluated to be of 6.5\% by selecting events passing all our selection cuts but 
originating from different vertices. The $\pi^0$ contamination was estimated 
using detector simulation and experimental data. From simulation, we calculated 
the ratio ($R = N^{1\gamma}_{sim}/N^{2\gamma}_{sim}$) of the number of $\pi^0$ 
events that are wrongly identified as exclusive $ep\rightarrow e'p'\gamma$ 
events to the number of events correctly identified as exclusive $ep\rightarrow 
e'p'\pi^0$.  Then in each kinematical bin and for each beam-helicity state, the 
$\pi^0$-subtracted experimental DVCS events is calculated as $N = 
N^{ep\rightarrow e'p'\gamma}_{exp}- R~N^{ep\rightarrow e'p'\pi^0}_{exp}$, where 
$N^{ep\rightarrow e'p'\gamma}_{exp}$ ($N^{ep\rightarrow e'p'\pi^0}_{exp}$) is 
the number of the experimentally identified $ep\rightarrow e'p'\gamma$ 
($ep\rightarrow e'p'\pi^0$) events. Depending on the kinematics, we found this 
contamination to be of 8 to 10\%.

%asymmetries
Experimentally, $A_{LU}$ is defined as
\begin{equation}
A_{LU} = \frac{1}{P_{B}} \frac{N^{+} - N^{-}}{N^{+} + N^{-} }.
\end{equation}
where $N^{+}$ and $N^{-}$ are the number of DVCS events for positive and negative 
beam-helicity state, and $P_{B}$ is the longitudinal beam polarization.

In the kinematical phase-space of our experiment, the GPD $H$ is
expected to dominate the contribution in the BSA over the other three GPDs.  
There, the $\phi$ dependence of $A_{LU}$ is mostly sensitive to the  imaginary 
part of the CFF $\mathcal{H}$ through the parameter $a_0$ of 
equation~\ref{eq:alu-simp}. The measurement of the free proton $A_{LU}$ 
\cite{Girod:2007aa} has confirmed that the $a_0$ term is dominating the shape 
of the distribution.

Due to limited statistics, the data were binned two-dimensionally into 36 bins.  
That is, four bins in one of the kinematical variable of interest ($Q^{2}$, 
$x_{B}$, or $t$) and then nine bins in the azimuthal angle ($\phi$).   
FIG.~\ref{fig:alu} presents the measured incoherent $A_{LU}$ as a function of 
$\phi$ in bins of $Q^{2}$ (integrated over full $x_{B}$ and $t$ ranges), 
$x_{B}$ (integrated over full $Q^{2}$ and $t$ ranges), and $t$ (integrated over 
full $Q^{2}$ and $x_{B}$ ranges). The curves on the plots are fits of the form 
$\frac{a_{0}~sin(\phi)}{1+ a_{1}~cos(\phi)}$.  The main contributions to 
systematic uncertainties on these fits are from the choice of the DVCS 
exclusivity cuts (6\%) and the large bin size (7\%). The systematic 
uncertainties sum up to less than 10\% for all data points and thus always 
remain significantly smaller than the statistical errors.

\begin{figure}[tb]
\includegraphics[width=8.9cm]{figs/incoherent_ALU_phi.pdf}
\caption{The incoherent $A_{LU}$ as a function of $\phi$. Results are presented
   for different $Q^{2}$ bins (top panel), $x_{B}$ bins (middle panel), and 
   $-t$ bins (bottom panel). The error bars represent the statistical 
   uncertainties. The gray bands represent the systematic uncertainties, 
   including the normalization uncertainties. The black curves are the results 
   of our fits with the form $\frac{a_{0}~sin(\phi)}{1+ a_{1}~cos(\phi)}$.}
\label{fig:alu}
\end{figure}

FIG.~\ref{fig:alu90} presents the dependence of the fitted $A_{LU}$ values at 
$\phi$~=~90$^{\circ}$ ($a_{0}$ parameter from the individual fits in 
FIG.~\ref{fig:alu}) on the kinematical variables $Q^2$, $x_{B}$, and $t$.  
Within the given uncertainties, $A_{LU}$ does not indicate a strong dependence 
on $Q^2$.  The $x_{B}$ and $t$ dependencies are compared to theoretical 
calculations performed by S.~Liuti and K.~Taneja \cite{simonetta_2}. Their 
model uses a nuclear spectral function and considers mainly off-shell effects.  
The calculations are carried out at slightly different kinematics than our data 
but still provide important guidance. The experimental results appear to have 
smaller asymmetries especially at small $x_{B}$ than the calculations. These 
differences may arise from nuclear effects which are not taken into account in 
the model, such as long-range interactions and final state interactions of the 
knock-out proton. On the graph for $-t$ dependence, we show previous 
measurements by the HERMES collaboration \cite{Airapetian:2009cga}, in which 
only electrons and photons were measured. Due to the large experimental 
uncertainties of the HERMES points, the two measurements are completely 
compatible.

>>>>

\date{\today}
\begin{abstract}
 We report the first beam spin asymmetry (BSA) measurement of incoherent deeply 
   virtual Compton scattering (DVCS) off $^4$He. The data were accumulated 
   using a 6 GeV longitudinally polarized electron beam incident on a 
   pressurized $^4$He gaseous target placed within the CLAS spectrometer in 
   Hall-B at the Thomas Jefferson National Accelerator Facility. The azimuthal 
   angle ($\phi$) dependence of the BSA was studied in a wide range of virtual 
   photon and scattered proton kinematics. The $Q^2$, $x_B$, and $t$ 
   dependencies of the BSA on the bound proton are compared with those on the 
   free proton. In the whole kinematical region of our measurements, the BSA on 
   the bound proton is smaller by $20\%$ to $40\%$, indicating possible medium 
   modification of its partonic structure. This measurement opens a new avenue 
   for studying the structure of bound nucleons and for exploring the origin of 
   the EMC effect using the framework of the generalized parton distributions.

@@

A wealth of information on the structure of hadrons lies in the correlations 
between the momentum and spatial degrees of freedom of the partons. These 
correlations can be revealed through deeply virtual Compton scattering (DVCS), 
i.e., the hard exclusive lepto-production of a real photon, which provides 
access to a three-dimensional (3-D) imaging of partons within the generalized 
parton distributions (GPDs) framework 
\cite{Mueller:1998fv,Ji:1996ek,Ji:1996nm,Radyushkin:1996nd,Radyushkin:1997ki}.   
The measurement of free proton DVCS has been the focus of a worldwide effort 
\cite{Stepanyan:2001sm,Airapetian:2001yk,Airapetian:2006zr,Chekanov:2003ya,Aktas:2005ty,Chen:2006na,Defurne:2015kxq,Girod:2007aa,Mazouz:2007aa,Gavalian:2009,Seder:2015,Pisano:2015,Jo:2015ema}
involving several accelerator facilities such as Jefferson Lab, DESY and  
CERN. These measurements now enable the extractions of GPDs 
and a 3-D tomography of the free proton \cite{Guidal:2013rya,Dupre:2016mai}.  
New measurements of DVCS from the $^{4}$He nucleus are a critical step towards 
providing a similar 3-D picture of the quark structure of the 
nucleus~\cite{Dupre:2015jha}. In the nuclear case, however, two channels are 
available, the coherent channel where the scattering is off the entire nucleus, 
which is left intact in the final state \cite{Airapetian:2009cga,
Hattawy:2017woc}, and the incoherent channel where the DVCS occurs on a 
nucleon, which is ejected from the nucleus. The latter is the focus of this 
letter and provides a unique access to the modification of the partonic 
structure of the bound nucleons \cite{simonetta_2,Guzey:2006xi,Guzey:2008fe}.  
The $^{4}$He nucleus is an ideal experimental target for this measurement as it 
is characterized by a strong binding energy, a relatively high nuclear core 
density, and a large EMC effect~\cite{JSeely}. Moreover, it remains simple 
enough that precise calculation of its structure can be performed, making this 
nucleus the perfect target for our investigation of the medium modifications of 
the nucleon's partonic structure.

\begin{figure}[tb]
\includegraphics[width=7.5cm]{figs/handbag_incoherent.pdf}
\caption{Representation of the leading-order, twist-2, handbag diagram of the 
   incoherent DVCS process off $^4$He, where the four-vectors of the electrons, 
   photons, and protons are denoted by $k/k^\prime$, $q/q^\prime$, and 
   $p/p^\prime$, respectively. $x+\xi$ is the nucleon longitudinal momentum 
   fraction carried by the struck quark, -2$\xi$ is the longitudinal momentum 
   fraction of the momentum transfer $\Delta$ ($= q - q^\prime$), and 
   $t$~($=\Delta^2$) is the squared momentum transfer between the initial and
   the final state nucleon.}
\label{fig:diags}
\end{figure}

In this Letter, we present the first exclusive measurement of the beam-spin 
asymmetry (BSA) in deeply virtual electroproduction of a real photon off a bound 
proton in $^{4}$He. FIG.~\ref{fig:diags} illustrates the leading-twist handbag 
diagram for the DVCS process. In the Bjorken regime, i.e. large virtual photon 
four-momentum squared ($Q^{2}=-q^2=-(k-k^\prime)^2$), and at small invariant 
momentum transfer ($t=(q-q^\prime)^2$), the DVCS scattering process can be 
factorized, leaving the non-perturbative structure of the nucleon to be 
parameterized in terms of four chirally even GPDs: $H$, $E$, $\widetilde{H}$, 
and $\widetilde{E}$, representing the four helicity-spin combinations of the 
quark-nucleon states \cite{Freund_Collins,Ji_Osborne}. Experimentally, we 
measure the squared sum of the Bethe-Heitler (BH) and the DVCS amplitudes. The 
BH process, where the real photon is emitted by the incident or the scattered 
electron rather than the nucleon, dominates the cross section at our 
kinematics. The BSA arises from the interference of these two terms and is 
directly sensitive to the DVCS amplitude that contains the information on the 
GPDs. Using a longitudinally polarized electron beam (L) and an unpolarized 
target (U), the BSA is defined as:
\begin{equation}
  A_{LU} = \frac{d^{5}\sigma^{+} - d^{5}\sigma^{-} }
                {d^{5}\sigma^{+} + d^{5}\sigma^{-}},
    \label{BSA_equation}
  \end{equation}
where $d^{5}\sigma^{+}$($d^{5}\sigma^{-}$) is the photon electroproduction 
differential cross section for a positive (negative) beam helicity.

Following the cross section decomposition provided in \cite{Belitsky:2001ns}, 
the different components can be expressed in terms of Fourier coefficients 
associated with $\phi$-harmonics, where $\phi$ is the angle between the 
leptonic and the hadronic planes of the reaction. At leading-twist, the BSA can 
be parameterized as: 
\begin{equation}
   A_{LU}(\phi) = \frac{a_{0}\sin(\phi)}{1+a_{1}\cos(\phi)+a_{2}\cos(2\phi)},
   \label{eq:alu-simp}
\end{equation}
where the parameters $a_{0,1,2}$ are combinations of the abovementioned Fourier 
coefficients. The $\sin(\phi)$ harmonic is dominant in $A_{LU}$ and is 
proportional to the following combination of Compton form factors (CFF) 
\cite{Guidal:2013rya}
\begin{equation}
   a_{0} \propto \operatorname{Im}( F_1 \mathcal{H}- \frac{t}{4M^2} F_2 
   \mathcal{E}+ \frac{x_B}{2}(F_1+F_2)\tilde{\mathcal{H}}),
\end{equation}
where $F_1$ and $F_2$ are the Dirac and Pauli form factors, respectively, and 
$x_B$ the Bjorken scaling variable. The real and the imaginary parts of the CFF 
$\mathcal{H}$ relate to the GPD $H$ as  \begin{align}
   \Re(&\mathcal{H}) = \mathcal{P} \int_{0}^{1}dx[H(x,\xi,t)-H(-x,\xi,t)] \, 
   C^{+}(x,\xi), \\
   \Im(&\mathcal{H}) = - \pi [H(\xi,\xi,t)-H(-\xi,\xi,t)],
\end{align}
with $\mathcal{P}$ the Cauchy principal value integral and $C^{+}$ a 
coefficient function defined as $(1/(x-\xi) + 1/(x+\xi))$, where $\xi$ is the 
skewing factor and can be related to $x_B$ by $\xi\approx {{x_B}\over{2-x_B}}$.  
Similar expressions apply for the GPDs $E$, $\widetilde{H}$, and 
$\widetilde{E}$ \cite{Guidal:2013rya}.

@@

The experiment (E08-024~\cite{Hafidi:2008pr}) took place in Hall-B of Jefferson 
Lab using the nearly 100\% duty factor, longitudinally polarized electron beam 
(83$\%$ polarization) from the Continuous Electron Beam Accelerator Facility 
(CEBAF) at an energy of 6.064 GeV. The data were accumulated over 40 days using 
a 6-atm-pressure, 292-mm-long, and 6-mm-diameter gaseous $^4$He target centered 
64~cm upstream of the CEBAF Large Acceptance Spectrometer (CLAS) coordinate 
center. For DVCS experiments, the CLAS baseline design \cite{Mecking:2003zu} 
was supplemented with an inner calorimeter (IC) and a solenoid magnet. The IC 
extended the photon detection acceptance of CLAS down to a polar angle of 
4$^{\circ}$. The 5-Tesla solenoid magnet in the center of which the target was 
located prevented the high-rate low-energy M{\o}ller electrons from reaching 
the CLAS drift chambers by guiding these electrons inside a tungsten shield 
placed around the beamline.

% DVCS selection
Incoherent DVCS events were selected by requiring an electron, a proton, and at 
least one photon in the final state. Electrons were identified as negatively 
charged tracks reconstructed in the drift chambers with an appropriate energy 
deposition in the electromagnetic calorimeter (EC) and a light yield above the 
threshold in the Cherenkov counters. The protons were identified from 
positively charged tracks based on their time-of-flight measured 
by the scintillator counters.  In addition, it was required that both the 
electron and the proton in the event originated from the same vertex at the 
target. The photons were detected in either the IC or the CLAS electromagnetic 
calorimeter. All the clusters within the IC fiducial region were assumed to be 
photons, while a timing cut was used to clean the EC photons from neutrons.  
Note that even though the DVCS reaction has only one real photon in the final 
state, events with more than one photon were not discarded at this stage. These 
extra photons were mostly soft photons from accidental coincidence which, as 
will be discussed below, the DVCS exclusivity cuts easily eliminated. In the 
following selection stage, the most energetic photon was considered as the DVCS 
photon candidate (see \cite{Hattawy:thesis} for additional details on the 
particle identification).

Further requirements were applied to clean the identified initial set of 
incoherent DVCS events from accidental and physics background events. First, 
events were selected with $Q^{2}$ greater than 1 GeV$^2$ to ensure the 
applicability of the DVCS handbag diagram, and with $\gamma^{*}p$ invariant 
mass ($W=\sqrt{(q+p)^2}$, assuming that the initial proton is at rest) greater 
than 2 GeV to avoid the nucleon resonance region. The squared transferred 
momentum to the recoil proton $t$, calculated from the four-momentum vectors of 
the incoming and outgoing photons, was required to be greater than a minimum 
kinematically allowed value at given $Q^2$ and 
$W$~($t>t_{min}(~=-Q^{2}~\frac{2(1-~x_{B})(1~-~\sqrt{1~+~\epsilon^{2}})~+~\epsilon~^{2}}{4x_{B}(1-x_{B})+\epsilon^{2}}$, 
where $\epsilon^{2}=~\frac{4M^{2}_{p}x^{2}_{B}}{Q^{2}}$ and $M_{p}$ is the 
proton mass). We specifically used the kinematics of the photons to determine 
$t$ because the initial proton kinematics is unknown due to Fermi motion. Then, 
we ensured the exclusivity of the incoherent DVCS events by imposing a series 
of constraints based on the four-momentum conservation in the reaction 
$ep\rightarrow e'p'\gamma$. These kinematical variables are: the coplanarity 
angle $\Delta\phi$ between the ($\gamma,\gamma^*$) and ($\gamma^*$,$p'$) 
planes, the missing energy, mass, and transverse momentum of the $e'\gamma$ and 
$e'p'\gamma$ systems, the missing mass squared of the $e'p'$ system, and the 
angle $\theta$ between the measured photon and the missing momentum of the 
$e'p'$ system. The experimental data for the most relevant exclusivity 
variables are shown in FIG.~\ref{fig:kin-cuts}. Because of the Fermi motion of 
the nucleons in the helium nucleus, these cuts
are slightly wider than those previously used for free proton experiments~%
\cite{Girod:2007aa}. After the corrections discussed below, the asymmetries 
appear to be stable as a function of cut width and we saw no sizable effect 
that could be related to the initial momentum of the nucleons. We also rejected 
events where a $\pi^0$ was identified by the invariant mass of two photons. At 
the end of this selection process, about 30k events passed all the 
requirements; their kinematic distributions are shown in 
FIG.~\ref{fig:kin-coverage}.

\begin{figure}[tb]
\includegraphics[width=8.9cm]{figs/incoh_exc_cuts_final.pdf}
\caption{The distributions from left to right and from top to bottom are: 
   $\Delta \phi$, missing energy, missing masses squared and the cone angle 
   ($\theta$) between the measured and the calculated photons in the $e'p'$ 
   final-state system. The incoherent DVCS exclusivity cuts are represented by 
   the vertical red-dashed lines. The black distributions represent the 
   incoherent DVCS event candidates before the exclusivity cuts. The shaded 
   distributions represent the incoherent DVCS events that passed all of these 
   cuts except the quantity plotted.}
\label{fig:kin-cuts}

@@

%background
The two main backgrounds that contributed to the event sample after the 
exclusivity cuts are due to accidental coincidences and exclusive $\pi^0$ 
production where one of the photons from the $\pi^0$ decay escapes detection.  
The contribution from accidental events, i.e., $e'p'\gamma$ collections with 
particles originating from different electron scatterings, was evaluated to be 
6.5\% by selecting events passing all our selection cuts but originating from 
different vertices. Our final asymmetries have been corrected for this 
contamination in the form of
$A_{LU~\text{corrected}}~=~\frac{1}{1~-~\text{contamination~percentage}}~A_{LU~\text{measured}}$. 
The $\pi^0$ contamination was estimated using detector simulation and 
experimental data. From simulation, we calculated the ratio ($R = 
N^{1\gamma}_{sim}/N^{2\gamma}_{sim}$) of the number of $\pi^0$ events that were 
wrongly identified as exclusive $ep\rightarrow e'p'\gamma$ events to the number 
of events correctly identified as exclusive $ep\rightarrow e'p'\pi^0$.  Then in 
each kinematical bin and for each beam-helicity state, the $\pi^0$-subtracted 
experimental DVCS events were calculated as $N = N^{ep\rightarrow 
e'p'\gamma}_{exp}- R~N^{ep\rightarrow e'p'\pi^0}_{exp}$, where 
$N^{ep\rightarrow e'p'\gamma}_{exp}$ ($N^{ep\rightarrow e'p'\pi^0}_{exp}$) is 
the number of the experimentally identified $ep\rightarrow e'p'\gamma$ 
($ep\rightarrow e'p'\pi^0$) events.  Depending on the kinematics, we found this 
contamination to be 8 to 10\%.

%asymmetries
Experimentally, $A_{LU}$ is defined as
\begin{equation}
A_{LU} = \frac{1}{P_{B}} \frac{N^{+} - N^{-}}{N^{+} + N^{-} },
\end{equation}
where $N^{+}$ and $N^{-}$ are the number of DVCS events for the positive and 
negative beam-helicity states, and $P_{B}$ is the longitudinal beam 
polarization.

In the kinematical phase-space of our experiment, the GPD $H$ is
expected to dominate the contribution in the BSA over the other three GPDs.  
There, the $\phi$ dependence of $A_{LU}$ is mostly sensitive to the  imaginary 
part of the CFF $\mathcal{H}$ through the parameter $a_0$ of 
equation~\ref{eq:alu-simp}. The measurement of the free proton $A_{LU}$ 
\cite{Girod:2007aa} has confirmed that the $a_0$ term dominates the shape of 
the distribution.

Due to limited statistics, the data were binned two-dimensionally into 36 bins.  
That is, four bins in one of the kinematical variable of interest ($Q^{2}$, 
$x_{B}$, or $t$) and then nine bins in the azimuthal angle ($\phi$).   
FIG.~\ref{fig:alu} presents the measured incoherent $A_{LU}$ as a function of 
$\phi$ in bins of $Q^{2}$ (integrated over the full $x_{B}$ and $t$ ranges), 
$x_{B}$ (integrated over the full $Q^{2}$ and $t$ ranges), and $t$ (integrated 
over the full $Q^{2}$ and $x_{B}$ ranges). The curves on the plots are fits of 
the form $\frac{a_{0}~\sin(\phi)}{1+ a_{1}~\cos(\phi)}$.  The main 
contributions to systematic uncertainties on these fits are from the choice of 
the DVCS exclusivity cuts (6\%) and the large bin size (7\%). The systematic 
uncertainties sum up to less than 10\% for all data points and thus always 
remain significantly smaller than the statistical uncertainities.

\begin{figure}[tb]
\includegraphics[width=8.9cm]{figs/incoherent_ALU_phi.pdf}
\caption{The incoherent $A_{LU}$ as a function of $\phi$. Results are presented
   for different $Q^{2}$ bins (top row), $x_{B}$ bins (middle row), and $-t$ 
   bins (bottom row). The error bars represent the statistical uncertainties.  
   The gray bands represent the systematic uncertainties, including the 
   normalization uncertainties. The black curves are the results of our fits 
   with the form $\frac{a_{0}~\sin(\phi)}{1+ a_{1}~\cos(\phi)}$.}
\label{fig:alu}
\end{figure}

FIG.~\ref{fig:alu90} presents the dependence of the fitted $A_{LU}$ values at 
$\phi$~=~90$^{\circ}$ ($a_{0}$ parameter from the individual fits in 
FIG.~\ref{fig:alu}) on the kinematical variables $Q^2$, $x_{B}$, and $t$.  
Within the given uncertainties, $A_{LU}$ does not show a strong dependence on 
$Q^2$.  The $x_{B}$ and $t$ dependencies are compared to the theoretical 
calculations performed by S.~Liuti and K.~Taneja \cite{simonetta_2}. Their 
model uses a nuclear spectral function and considers mainly off-shell effects.  
The calculations are carried out at slightly different kinematics than our data 
but still provide important guidance. The experimental results appear to have 
smaller asymmetries especially at small $x_{B}$ than the calculations. These 
differences may arise from nuclear effects that are not taken into account in 
the model, such as long-range interactions and final state interactions of the 
knocked-out proton. On the graph for the $-t$ dependence, we show previous 
measurements by HERMES collaboration \cite{Airapetian:2009cga}, in which only 
electrons and photons were measured. Due to the large experimental 
uncertainties of the HERMES points, the two measurements are completely 
compatible.
